**Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces**

### 2020-03-09 submission/manuscript.Rmd
Additional discussion.

Sequencing of the 16S rRNA V4 region yielded a total of `r million_sequences` million sequences after quality curation and exclusion of eukaryotic, chloroplast, mitochondrial and no relative sequences (\autoref{supp-nseq_notus}). A total of `r samples_epiphytes` samples originating from epiphytic archaeal and bacterial communities associated with surfaces of the seagrass *Cymodocea nodosa* and macroalga *Caulerpa cylindracea* were analyzed. In addition, `r samples_seawater` samples (one of the samples was sequenced two times) originating from picoplankton archaeal and bacterial communities in the surrounding seawater were also processed. The number of reads per sample ranged between `r min_max$min` and `r min_max$max` sequences (\autoref{supp-nseq_notus}). Even when the highest sequencing effort was applied the rarefaction curves did not level off that is a common observation in high-throughput 16S rRNA amplicon sequencing approaches (\autoref{supp-rarefaction}). Following quality curation and exclusion of sequences mentioned before reads were clustered into `r no_otus` different OTUs at a similarity level of 97 \si{\percent}. Reads numbers were normalized to the minimum number of sequences, `r min_max$min` (\autoref{supp-nseq_notus}), through rarefaction resulting in `r no_otus_rarefied` different OTUs that ranged from `r min(otu_min_max)` to `r max(otu_min_max)` OTUs per sample (\autoref{supp-calculators}). To determine seasonal changes of richness and diversity the Observed Number of OTUs, Chao1, ACE, Exponential Shannon [@Jost2006] and Inverse Simpson were calculated after normalization through rarefaction. Generally, richness estimators and diversity indices showed similar trends. On average, higher values were found for *Caulerpa cylindracea* (invaded [Number of OTUs, `r S.obs_fcam$mean` ± `r S.obs_fcam$sd` OTUs] and noninvaded [Number of OTUs, `r S.obs_fca$mean` ± `r S.obs_fca$sd` OTUs]), middle vales for *Cymodocea nodosa* (Number of OTUs, `r S.obs_fcym$mean` ± `r S.obs_fcym$sd` OTUs) and lower values for picoplankton communities in the surrounding seawater (Number of OTUs, `r S.obs_f$mean` ± `r S.obs_f$sd` OTUs) (\autoref{supp-calculators}). Seasonal changes did not show such large dissimilarities. Seawater communities richness was stable during the studied period with the exception of one sampling point in December 2017 when larger values were observed. *Cymodocea nodosa* communities showed a slow increase towards the end of the study, while *Caulerpa cylindracea* (invaded and noninvaded) communities were characterized by slightly larger values in Spring and Summer in comparison to Autumn and Winter (\autoref{supp-calculators}).

@@

metadata_rarefied_select <- metadata_rarefied %>%
  filter(station=="F") %>%
  select(starts_with("Otu"))
grouping <- metadata_rarefied %>%
  filter(station=="F") %>%
  mutate(grouping=str_replace(season, "Autumn", "Winter"))
anosim_f <- anosim(metadata_rarefied_select, grouping$grouping, permutations=1000, distance="bray")
anosim_f_signif <- case_when(anosim_f$signif < 0.05 & anosim_f$signif >= 0.01 ~ 0.05,
                             anosim_f$signif < 0.01 & anosim_f$signif >= 0.001 ~ 0.01,
                             anosim_f$signif < 0.001 & anosim_f$signif >= 0.0001 ~ 0.001,
                             anosim_f$signif < 0.0001 ~ 0.0001,
                             TRUE ~ anosim_f$signif)

@@

To determine the proportion of shared archaeal and bacterial OTUs and communities sampled in different environments the Jaccard's Similarity Coefficient on presence-absence data and Bray-Curtis Similarity Coefficient were, respectively, calculated. Coefficients were determined after normalization through rarefaction and binning of samples from a particular environment. The highest proportion of shared OTUs and community was found between invaded and noninvaded  *Caulerpa cylindracea* (Jaccard, `r format(filter(similarity, V1=="FCa", V2=="FCaM")$jaccard, digits=2, nsmall=2)`; Bray-Curtis, `r format(filter(similarity, V1=="FCa", V2=="FCaM")$bray, digits=2, nsmall=2)`), while lower shared values were calculated between seawater and epiphytic communities (\autoref{matrix}). Shared proportion between *Cymodocea nodosa* and *Caulerpa cylindracea* were approximately in the middle between these two extremes. To assess seasonal changes in the proportion of shared OTUs and communities the Jaccard's and Bray-Curtis Similarity Coefficients were calculated between consecutive sampling points (\autoref{shared}). Both coefficients showed similar trends. Temporal proportional changes were more pronounced for seawater in comparison to *Cymodocea nodosa* and especially *Caulerpa cylindracea* associated communities (\autoref{shared}). In addition, only `r min(core$core_otus)` -- `r max(core$core_otus)` \si{\percent} of OTUs from each surface associated community were found at every time point. These OTUs made also a high proportion of total sequences (`r min(core$core_seq)` -- `r max(core$core_seq)` \si{\percent}). To further disentangle the environmental and seasonal community dissimilarity a Principal Coordinates Analysis (PCoA) based on Bray-Curtis distances and OTU abundances was applied. It showed a clear separation between planktonic and surface associated communities (\autoref{pcoa}). In addition, a separation of epiphytic bacterial and archaeal communities based on host species was determined. This separation was further supported by ANOSIM (R = `r format(anosim_all$statistic, digits=2, nsmall=2)`, *p* < `r anosim_all_signif`). Seasonal changes of seawater communities indicated a separation between Spring, Summer and Autumn/Winter samples (ANOSIM, R = `r format(anosim_f$statistic, digits=2, nsmall=2)`, *p* < `r anosim_f_signif`). Epiphytic microbial communities associated with *Cymodocea nodosa* showed a similar pattern (ANOSIM, R = `r format(anosim_fcym$statistic, digits=2, nsmall=2)`, *p* < `r anosim_fcym_signif`), while communities from the surfaces of *Caulerpa cylindracea* indicated a non so strongly supported, as in previous cases, separation between Summer and Autumn/Winter/Spring samples (ANOSIM, R = `r format(anosim_fca$statistic, digits=2, nsmall=2)`, *p* < `r anosim_fca_signif`) (\autoref{pcoa}).

@@

# Calculating the mean and standard deviation for each station
desulfo_station_whole <- inner_join(metadata, whole, by=c("ID"="Group")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  group_by(station) %>%
  summarise(mean=mean(abundance), sd=sd(abundance))

# Calculating the mean and standard deviation for contrasting season of Caulerpa cylindracea
desulfo_station_season_whole <- inner_join(metadata, whole, by=c("ID"="Group")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  filter(station=="FCaM" | station=="FCa") %>%
  mutate(season=str_replace(season, "Winter", "Summer")) %>%
  mutate(season=str_replace(season, "Spring", "Autumn")) %>%
  group_by(station, season) %>%
  summarise(mean=mean(abundance), sd=sd(abundance))
```

In contrast to previously described high rank taxa, *Desulfobacterota* were specific to *Caulerpa cylindracea*. On average they were comprising `r desulfo_all_whole$mean` ± `r desulfo_all_whole$sd` \si{\percent} of all sequences. While seawater and *Cymodocea nodosa* communities were consisted of only `r filter(desulfo_station_whole, station=="F")$mean` ± `r filter(desulfo_station_whole, station=="F")$sd` \si{\percent} and `r filter(desulfo_station_whole, station=="FCyM")$mean` ± `r filter(desulfo_station_whole, station=="FCyM")$sd` \si{\percent} *Desulfobacterota* sequences, respectively, in the invaded and noninvaded *Caulerpa cylindracea* communities their proportion was `r filter(desulfo_station_whole, station=="FCaM")$mean` ± `r filter(desulfo_station_whole, station=="FCaM")$sd` \si{\percent} and `r filter(desulfo_station_whole, station=="FCa")$mean` ± `r filter(desulfo_station_whole, station=="FCa")$sd` \si{\percent}, respectively (\autoref{desulfo}). In addition, *Caulerpa cylindracea* associated communities were characterized by higer proportions in Winter and Summer (invaded, `r filter(desulfo_station_season_whole, station=="FCaM", season=="Summer")$mean` ± `r filter(desulfo_station_season_whole, station=="FCaM", season=="Summer")$sd` \si{\percent}; noninvaded, `r filter(desulfo_station_season_whole, station=="FCa", season=="Summer")$mean` ± `r filter(desulfo_station_season_whole, station=="FCa", season=="Summer")$sd` \si{\percent}) in comparison to Autumn and Spring (invaded, `r filter(desulfo_station_season_whole, station=="FCaM", season=="Autumn")$mean` ± `r filter(desulfo_station_season_whole, station=="FCaM", season=="Autumn")$sd` \si{\percent}; noninvaded, `r filter(desulfo_station_season_whole, station=="FCa", season=="Autumn")$mean` ± `r filter(desulfo_station_season_whole, station=="FCa", season=="Autumn")$sd` \si{\percent}). The community was mainly consisted of no relative *Desulfobacteraceae*, *Desulfatitalea*, no relative *Desulfobulbaceae*, *Desulfobulbus*, no relative *Desulfocapsaceae*, *Desulfopila*, *Desulforhopalus*, *Desulfotalea*, SEEP-SRB4 and uncultured *Desulfocapsaceae* (\autoref{desulfo}).

@@

Since the colonization of macrophyte surfaces is performed from a pool of seawater prokaryotic cells it is interesting to see to which extent do these two communities differ. We observed a strong differentiation between the surface attached and seawater communities at the level of OTUs that is in agreement with most published studies [@Ugarelli2019; @Roth-Schulze2016; @Burke2011b; @Michelou2013]. These data indicate that marine macrophytes are selecting, from a pool of seawater microbial taxa, the one that can colonize and proliferate on their surfaces [@Salaun2012; @Michelou2013]. In contrast to these findings @Fahimipour2017 found, in a global study of *Zostera marina*, similarities between leaves and seawater samples. Discrepancies between our data and this study could be explained by differences in studied seagrass species, methodological variations or biogeographic trends as @Fahimipour2017 were analyzing samples from different locations throughout the northern hemisphere. It is possible that ambient seawater and leaves communities from the same location are differing but are still more similar to each other when compared to other sampling locations. Indeed, it was found that prokaryotic communities vary substantially between different sampling sites [@Bengtsson2017]. When the taxonomic composition at high ranks was analyzed no such strong differentiation was noticed. Phyla and classes such as: *Actinobacteriota*, *Bacteroidota*, *Cyanobacteria*, *Alphaproteobacteria*, *Gammaproteobacteria* and *Verrucomicrobiota*, were described that is in agreement with previously reported data [@Egan2013; @Michelou2013; @Burke2011b]. In contrast, when low taxonomic ranks were analyzed (i.g. family and genus) a strong differentiation was observed. A similar differentiation at lower taxonomic ranks was described for other species of macrophytes [@Egan2013; @Michelou2013; @Ugarelli2019].

@@

Few studies describing microbial epiphytic communities were encompassing seasonal shifts [@Lachnit2011; @Tujula2010; @Michelou2013]. Seasonal changes in the epiphytic community were substantial as could be observed in the proportion of OTUs that could be find at every sampling time ($\leqslant$ `r max(core$core_otus)` \si{\percent}). Interestingly, these OTUs were accounting for a high proportion of sequences ($\leqslant$ `r max(core$core_seq)` \si{\percent}). A very similar proportion of persistent OTUs and their sequence contribution was reported in high frequency studies describing seasonal picoplankton changes [@Gilbert2009; @Gilbert2012]. In comparison to the seawater community, a lower degree of seasonal shifts was observed for the surface associated communities. It seems, that microniches on the surfaces of macrophytes are providing more stable conditions in comparison to the seawater. At the level of OTUs seasonal changes of *Cymodocea nodosa* and *Caulerpa cylindracea* associated communities were identified that could be linked to the growth cycle of the seagrass and macroalgae (M. Najdek, personal communication). *Cymodocea nodosa* was characterized by a Spring community during maximum seagrass proliferation, a Summer community during a biomass maximum and a Autumn/Winter community during a biomass decay. In contrast, *Caulerpa cylindracea* started to proliferate in late Spring and was characterized only by a Summer community during maximal biomass increase and by a Autumn/Winter/Spring community when the biomass were at the peak and the settlement started to subsequently decay. Similar seasonal changes in the epiphytic community was described also for other macroalgae [@Lachnit2011; @Tujula2010]. The higher temporal stability of *Caulerpa cylindracea* surface communities in comparison to *Cymodocea nodosa* could be also observed in the higher proportion of shared communities between two consecutive sampling points.

@@

```{r out.width="100%", fig.align="center", fig.cap="Principal Coordinates Analysis (PCoA) of Bray-Curtis distances based on OTU abundances of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{Cymodocea nodosa} [Invaded] and \\textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater. Samples from the same environment or same season are labeld in different colors. The proportion of explained variation by each axis is shown on the corresponding axis in parentheses.\\label{pcoa}", fig.pos="H"}
include_graphics("../results/figures/pcoa_figure.jpg")
```

>>>>

Sequencing of the 16S rRNA V4 region yielded a total of `r million_sequences` million sequences after quality curation and exclusion of eukaryotic, chloroplast, mitochondrial and no relative sequences (\autoref{supp-nseq_notus}). A total of `r samples_epiphytes` samples originating from epiphytic archaeal and bacterial communities associated with surfaces of the seagrass *Cymodocea nodosa* and macroalga *Caulerpa cylindracea* were analyzed. In addition, `r samples_seawater` samples (one of the samples was sequenced two times) originating from picoplankton archaeal and bacterial communities in the ambient seawater were also processed for comparison. The number of reads per sample ranged between `r min_max$min` and `r min_max$max` sequences (\autoref{supp-nseq_notus}). Even when the highest sequencing effort was applied the rarefaction curves did not level off that is a common observation in high-throughput 16S rRNA amplicon sequencing approaches (\autoref{supp-rarefaction}). Following quality curation and exclusion of sequences mentioned before reads were clustered into `r no_otus` different OTUs at a similarity level of 97 \si{\percent}. Reads numbers were normalized to the minimum number of sequences, `r min_max$min` (\autoref{supp-nseq_notus}), through rarefaction resulting in `r no_otus_rarefied` different OTUs that ranged from `r min(otu_min_max)` to `r max(otu_min_max)` OTUs per sample (\autoref{supp-calculators}). To determine seasonal changes of richness and diversity the Observed Number of OTUs, Chao1, ACE, Exponential Shannon [@Jost2006] and Inverse Simpson were calculated after normalization through rarefaction. Generally, richness estimators and diversity indices showed similar trends. On average, higher values were found for *Caulerpa cylindracea* (invaded [Number of OTUs, `r S.obs_fcam$mean` ± `r S.obs_fcam$sd` OTUs] and noninvaded [Number of OTUs, `r S.obs_fca$mean` ± `r S.obs_fca$sd` OTUs]), middle vales for *Cymodocea nodosa* (Number of OTUs, `r S.obs_fcym$mean` ± `r S.obs_fcym$sd` OTUs) and lower values for picoplankton communities in the ambient seawater (Number of OTUs, `r S.obs_f$mean` ± `r S.obs_f$sd` OTUs) (\autoref{supp-calculators}). Seasonal changes did not show such large dissimilarities. *Cymodocea nodosa* communities showed a slow increase towards the end of the study, while *Caulerpa cylindracea* (invaded and noninvaded) communities were characterized by slightly larger values in Spring and Summer in comparison to Autumn and Winter (\autoref{supp-calculators}).

@@

@@

To determine the proportion of shared archaeal and bacterial OTUs and communities sampled in different environments the Jaccard's Similarity Coefficient on presence-absence data and Bray-Curtis Similarity Coefficient were, respectively, calculated. Coefficients were determined after normalization through rarefaction and binning of samples from a particular environment. The highest proportion of shared OTUs and community was found between invaded and noninvaded  *Caulerpa cylindracea* (Jaccard, `r format(filter(similarity, V1=="FCa", V2=="FCaM")$jaccard, digits=2, nsmall=2)`; Bray-Curtis, `r format(filter(similarity, V1=="FCa", V2=="FCaM")$bray, digits=2, nsmall=2)`), while lower shared values were calculated between seawater and epiphytic communities (\autoref{matrix}). Shared proportion between *Cymodocea nodosa* and *Caulerpa cylindracea* were approximately in the middle between these two extremes. To assess seasonal changes in the proportion of shared OTUs and communities the Jaccard's and Bray-Curtis Similarity Coefficients were calculated between consecutive sampling points (\autoref{shared}). Both coefficients showed similar trends. Temporal proportional changes were more pronounced for seawater in comparison to *Cymodocea nodosa* and especially *Caulerpa cylindracea* associated communities (\autoref{shared}). In addition, only `r min(core$core_otus)` -- `r max(core$core_otus)` \si{\percent} of OTUs from each surface associated community were found at every time point. These OTUs made also a high proportion of total sequences (`r min(core$core_seq)` -- `r max(core$core_seq)` \si{\percent}). To further disentangle the environmental and seasonal community dissimilarity a Principal Coordinates Analysis (PCoA) based on Bray-Curtis distances and OTU abundances was applied. It showed a clear separation between planktonic and surface associated communities (\autoref{pcoa}). In addition, a separation of epiphytic bacterial and archaeal communities based on host species was determined. This separation was further supported by ANOSIM (R = `r format(anosim_all$statistic, digits=2, nsmall=2)`, *p* < `r anosim_all_signif`). Seasonal changes of *Cymodocea nodosa* associated communities indicated a separation between Spring, Summer and Autumn/Winter samples (ANOSIM, R = `r format(anosim_fcym$statistic, digits=2, nsmall=2)`, *p* < `r anosim_fcym_signif`), while communities from the surfaces of *Caulerpa cylindracea* indicated a non so strongly supported, as in previous cases, separation between Summer and Autumn/Winter/Spring samples (ANOSIM, R = `r format(anosim_fca$statistic, digits=2, nsmall=2)`, *p* < `r anosim_fca_signif`) (\autoref{pcoa}).

@@

# Calculating the mean and standard deviation for each station
desulfo_station_whole <- inner_join(metadata, whole, by=c("ID"="Group")) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  group_by(station) %>%
  summarise(mean=mean(abundance), sd=sd(abundance))
```

In contrast to previously described high rank taxa, *Desulfobacterota* were specific to *Caulerpa cylindracea*. On average they were comprising `r desulfo_all_whole$mean` ± `r desulfo_all_whole$sd` \si{\percent} of all sequences. While seawater and *Cymodocea nodosa* communities were consisted of only `r filter(desulfo_station_whole, station=="F")$mean` ± `r filter(desulfo_station_whole, station=="F")$sd` \si{\percent} and `r filter(desulfo_station_whole, station=="FCyM")$mean` ± `r filter(desulfo_station_whole, station=="FCyM")$sd` \si{\percent} *Desulfobacterota* sequences, respectively, in the invaded and noninvaded *Caulerpa cylindracea* communities their proportion was `r filter(desulfo_station_whole, station=="FCaM")$mean` ± `r filter(desulfo_station_whole, station=="FCaM")$sd` \si{\percent} and `r filter(desulfo_station_whole, station=="FCa")$mean` ± `r filter(desulfo_station_whole, station=="FCa")$sd` \si{\percent}, respectively (\autoref{desulfo}). The community was mainly consisted of no relative *Desulfobacteraceae*, *Desulfatitalea*, no relative *Desulfobulbaceae*, *Desulfobulbus*, no relative *Desulfocapsaceae*, *Desulfopila*, *Desulforhopalus*, *Desulfotalea*, SEEP-SRB4 and uncultured *Desulfocapsaceae* (\autoref{desulfo}).

@@

Since the colonization of macrophyte surfaces is performed from a pool of seawater prokaryotic cells it is interesting to see to which extent do these two communities differ. We observed a strong differentiation between the surface attached and seawater communities at the level of OTUs that is in agreement with most published studies [@Ugarelli2019; @Roth-Schulze2016; @Burke2011b; @Michelou2013; @Crump2018]. These data indicate that marine macrophytes are selecting, from a pool of seawater microbial taxa, the one that can colonize and proliferate on their surfaces [@Salaun2012; @Michelou2013]. In contrast to these findings @Fahimipour2017 found, in a global study of *Zostera marina*, similarities between leaves and seawater samples. Discrepancies between our data and this study could be explained by differences in studied seagrass species, methodological variations or biogeographic trends as @Fahimipour2017 were analyzing samples from different locations throughout the northern hemisphere. It is possible that ambient seawater and leaves communities from the same location are differing but are still more similar to each other when compared to other sampling locations. Indeed, it was found that prokaryotic communities vary substantially between different sampling sites [@Bengtsson2017]. When the taxonomic composition at high ranks was analyzed no such strong differentiation was noticed. Phyla and classes such as: *Actinobacteriota*, *Bacteroidota*, *Cyanobacteria*, *Alphaproteobacteria*, *Gammaproteobacteria* and *Verrucomicrobiota*, were described that is in agreement with previously reported data [@Egan2013; @Michelou2013; @Burke2011b]. In contrast, when low taxonomic ranks were analyzed (i.g. family and genus) a strong differentiation was observed. A similar differentiation at lower taxonomic ranks was described for other species of macrophytes [@Egan2013; @Michelou2013; @Ugarelli2019].

@@

Seasonal richness changes in the epiphytic community were substantial as could be observed in the proportion of OTUs that could be find at every sampling time ($\leq$ `r max(core$core_otus)` \si{\percent}). Interestingly, these OTUs were accounting for a high proportion of sequences ($\leq$ `r max(core$core_seq)` \si{\percent}). A very similar proportion of persistent OTUs and their sequence contribution was reported in high frequency studies describing seasonal picoplankton changes [@Gilbert2009; @Gilbert2012]. In comparison to the seawater community, a lower degree of seasonal shifts was observed for the surface associated communities. It seems, that microniches on the surfaces of macrophytes are providing more stable conditions in comparison to the seawater. At the level of OTUs seasonal changes of *Cymodocea nodosa* and *Caulerpa cylindracea* associated communities were identified that could be linked to the growth cycle of the seagrass and macroalgae (M. Najdek, personal communication). *Cymodocea nodosa* was characterized by a Spring community during maximum seagrass proliferation, a Summer community during a biomass maximum and a Autumn/Winter community during a biomass decay. In contrast, *Caulerpa cylindracea* started to proliferate in late Spring and was characterized only by a Summer community during maximal biomass increase and by a Autumn/Winter/Spring community when the biomass were at the peak and the settlement started to subsequently decay. Similar seasonal changes in the epiphytic community was described also for other macroalgae [@Lachnit2011; @Tujula2010]. Higher temporal stability of *Caulerpa cylindracea* surface communities in comparison to *Cymodocea nodosa* were also observed in the higher proportion of shared communities between two consecutive sampling points.

Seasonal patterns of high rank epiphytic taxa did not show strong changes. Only *Cyanobateria* were characterized by strong seasonal differences. Cyanobacterial sequences were more pronounced in the November and December 2017 in comparison to Spring and Summer. Interestingly, in these high proportion months the majority of cyanobacterial sequences were classified as *Pleurocapsa*, a group known to colonized different living and nonliving surfaces [@Longford2007; @Burns2004; @Mobberley2012; @Reisser2014]. It is possible than during periods of low metabolic activity of the i.g. seagrass there is no so active interaction and selection of the epiphytic community, so the seagrass leaves are becoming a suitable surface for nonspecific colonizers [@Zavodnik1998]. *Pleurocapsa* was replaced in Spring ans Summer by *Acrophormium*, *Phormidesmis* and no relative *Nodosilineaceae*. A study of coastal microbial mats found also higher proportion of *Nodosilineaceae* sequences in Summer, while *Phormidesmis* sequences were at their peak in Autumn [@Cardoso2019]. Other high rank taxa did not showed strong successional patterns. In each analyzed group low rank taxa

@@

```{r out.width="55%", fig.align="center", fig.cap="Principal Coordinates Analysis (PCoA) of Bray-Curtis distances based on OTU abundances of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{Cymodocea nodosa} [Invaded] and \\textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater. Samples from the same environment or same season are labeld in different colors. The proportion of explained variation by each axis is shown on the corresponding axis in parentheses.\\label{pcoa}", fig.pos="H"}
include_graphics("../results/figures/pcoa_figure.jpg")
```
